QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-09-12 paper.tex
Rev_RelatedWorkTable_V0.1

>>>>

\begin{table*}[htbp]
	\renewcommand{\arraystretch}{1}
	\captionsetup{name=TABLE}
	\caption{Simulation Parameters}
	\scalebox{1}{%
		\begin{tabular}{ lp{1.8cm}p{3cm}p{3.3cm}p{1cm}p{2.5cm}p{2.5cm}l} 
			\toprule
			\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Algorithm/Methods} &  \textbf{Drawbacks}  \\ \midrule
			\cite{huang2019deep} & Wireless-powered MEC & &  & & & \\
			\cite{Bolourian-WCL24} & Wireless-powered MEC & Computation offloading & Minimize drop rate and energy consumption. &  & & \\
			\cite{zhao2019deep} & MEC & Wireless channels competition & Optimize downlink utility &&& \\
			\cite{9253665} &  MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\
			\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay && hierarchical DRL & \\
			\cite{dai2020edge} & MEC & Resource allocation and computation offloading &&& & \\
			\cite{huang2021deadline} & MEC & & Minimizing total energy consumption & POMDP & & \\
			\cite{liu2021learn} & MEC & Resource allocation and computation offloading &&  & MADRL & \\
			\cite{zhou2021deep} & MEC & Resource allocation and computation offloading && MDP & Q-learning & \\
			\cite{gao2022large} & heterogeneous MEC & Decentralized computation offloading &&& & \\
			\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption && & \\
			\cite{liao2023online} & MEC & Online computation offloading & Minimize task computation delay and energy consumption && DDQN & \\
			\cite{wu2023multi} & MEC-based IIoT & Computation offloading & Optimization of delay and energy consumption & POMDP & Multi-agent DQN& \\
			\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & \\
			\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent Actor–critic network & \\
			\cite{wu2024combining} & MEC-based IIoT & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor–critic network  & \\
			QECO &  MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
			\toprule
	\end{tabular}}
	\label{table}
\end{table*}
